Merits of hypermedia systems

### 2014-02-03 dagstuhl-2013/position.tex
Fix refs
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@693 43ef1190-90fd-4dd7-a769-d0121f02b80e

\bibliographystyle{plain}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{federation,webarch,vocabs,specs,hypermedia,egne,selectivity}

>>>>

\begin{thebibliography}{1}

\bibitem{hypermediatypes}
Mike Amundsen.
\newblock {Hypermedia Types}.
\newblock \url{http://amundsen.com/hypermedia/}, 2010.

\bibitem{Fielding_2000_Architectural-Styles}
Roy~Thomas Fielding.
\newblock {\em Architectural Styles and the Design of Network-based Software
  Architectures}.
\newblock PhD thesis, {University of California, Irvine}, 2000.

\bibitem{splendid}
Olaf G\"{o}rlitz and Steffen Staab.
\newblock {SPLENDID: SPARQL Endpoint Federation Exploiting VOID Descriptions}.
\newblock In {\em Proceedings of the 2nd International Workshop on Consuming
  Linked Data}, Bonn, Germany, 2011.

\bibitem{kjernsmo_lapis_2012}
Kjetil Kjernsmo.
\newblock The necessity of hypermedia rdf and an approach to achieve it.
\newblock In {\em Proceedings of the First Linked APIs workshop at the Ninth
  Extended Semantic Web Conference}, May 2012.

\end{thebibliography}
